MODELLING THE CO-EVOLUTION OF TRADE AND CULTURE IN PAST SOCIETIES

### 2015-07-22 article.tex
version sumbimett

Unbiased \emph{cultural transmission} is implemented using ``random copy'': each agent has a low probability to pick randomly one agent among all and copy its vector of values. The \emph{innovation} process, termed ``unbounded'', is triggered with a low probability ($\mu$) and draw a new random value to replace an element $v^i_j$. The probabilities to trigger \emph{cultural transmission} and \emph{innovation} are presented with other parameters in table~\ref{tab:parameters}.

@@

The neutral model is tested through 15 experimental setups. The first six experimental setups are using 1 good, two population sizes (250 and 500 agents) and three values of $\mu$ (0.004,0.016 and 0.064). The remaining experimental setups are using 500 agents, 3 number of goods (3,6 and 9) and three values of $\mu$ (0.004,0.016 and 0.064). For each setup, we have performed 100 runs of 10000 timestep each. The trading model is tested on an experimental setups using 3 goods, 500 agents and $\mu$ equal to 0.004. Again 100 runs of 10000 timesteps are performed. The complete set of parameters tested on both models is presented in table~\ref{tab:parameters}. The experiments are \href{https://github.com/montanier/CMR-WSC-CoEvolutionTradeCulture}{available online} \cite{github_2015} for the Pandora simulator~\cite{rubiocampillo_2014}.

@@

\begin{table}
\caption{Table of parameters}\label{tab:parameters}
	\scriptsize
\begin{center}
\begin{tabular}{@{}ll@{}}
\toprule
Parameter & Value \\
\midrule
Number of goods & $\{1,3,6,9\}$ \\
Number of agents & $\{250,500\}$ \\
Innovation probability ($\mu$) & $\{0.004,0.016,0.064\}$ \\
Innovation range ($\beta$) & 0.005\\
Cultural transmission probability & .001\\
CulturalStep &  10 \\
TradeThreshold & 100  \\
TimeSteps & 10000 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

@@

\section*{AUTHOR BIOGRAPHIES}
\noindent {\bf SIMON CARRIGNON} is a PhD student in Computer Applications in Science and Engineering, Barcelona Supercomputing Center. He holds a M.S. in Cognitive Sciences and a M.A. in History and Philosophy of Science. His works focused on the use of computer modeling and evolutionary method to study Complex Systems, ranging from Evolutionary Biology to Human and Cultural Dynamics. His email address is \email{simon.carrignon@bsc.es}.

\noindent {\bf JEAN-MARC MONTANIER} is Researcher in Computer Applications in Science and Engineering, Barcelona Supercomputing Center. He has obtained his engineering title in the domain of embedded computing and holds a Ph.D. in collective robotics. His topics of interest focused on Agent-Based Modeling, swarm adaptation, learning of cooperative strategies, division of labour and more recently study of economical and cultural evolution. His email address is \email{jean.montanier@bsc.es}.

\noindent {\bf XAVIER RUBIO-CAMPILLO} is Researcher in Computer Applications in Science and Engineering, Barcelona Supercomputing Center. He has a transdisciplinary training of Computer Science (BSc) and Humanities (PhD) with a strong emphasis on the study of past societies using historical and archaeological contexts. His main research line is the application of formal models to explore the processes of cultural evolution in past societies. His email address is \email{xavier.rubio@bsc.es}.

>>>>

Unbiased \emph{cultural transmission} is implemented using ``random copy'': each agent has a low probability to pick randomly one agent among all and copy its vector of values. The \emph{innovation} process, termed ``unbounded'', is triggered with a low probability ($\mu$) and draw a new random value to replace an element $v^i_j$. %The probabilities to trigger \emph{cultural transmission} and \emph{innovation} are presented with other parameters in table~\ref{tab:parameters}.

@@

The neutral model is tested through 15 experimental setups. The first six experimental setups are using 1 good, two population sizes (250 and 500 agents) and three values of $\mu$ (0.004,0.016 and 0.064). The remaining experimental setups are using 500 agents, 3 number of goods (3,6 and 9) and three values of $\mu$ (0.004,0.016 and 0.064). For each setup, we have performed 100 runs of 10000 timestep each. The trading model is tested on an experimental setups using 3 goods, 500 agents and $\mu$ equal to 0.004. Again 100 runs of 10000 timesteps are performed. The experiments, as well as the parameters used to run those experiments, are \href{https://github.com/montanier/CMR-WSC-CoEvolutionTradeCulture}{available online} \cite{github_2015} for the Pandora simulator~\cite{rubiocampillo_2014}.

@@

%\begin{table}
%\caption{Table of parameters}\label{tab:parameters}
%	\scriptsize
%\begin{center}
%\begin{tabular}{@{}ll@{}}
%\toprule
%Parameter & Value \\
%\midrule
%Number of goods & $\{1,3,6,9\}$ \\
%Number of agents & $\{250,500\}$ \\
%Innovation probability ($\mu$) & $\{0.004,0.016,0.064\}$ \\
%Innovation range ($\beta$) & 0.005\\
%Cultural transmission probability & .001\\
%CulturalStep &  10 \\
%TradeThreshold & 100  \\
%TimeSteps & 10000 \\
%\bottomrule
%\end{tabular}
%\end{center}
%\end{table}

@@

\section*{AUTHOR BIOGRAPHIES}
\noindent {\bf SIMON CARRIGNON} is a PhD student in Computer Applications in Science and Engineering, Barcelona Supercomputing Center. He holds a M.S. in Cognitive Sciences and a M.A. in History and Philosophy of Science. His works focused on the use of computer modeling and evolutionary method to study Complex Systems, ranging from Evolutionary Biology to Human and Cultural Dynamics. His email address is \email{simon.carrignon@bsc.es}.\\

\noindent {\bf JEAN-MARC MONTANIER} is Researcher in Computer Applications in Science and Engineering, Barcelona Supercomputing Center. He has obtained his engineering title in the domain of embedded computing and holds a Ph.D. in collective robotics. His topics of interest focused on Agent-Based Modeling, swarm adaptation, learning of cooperative strategies, division of labour and more recently study of economical and cultural evolution. His email address is \email{jean.montanier@bsc.es}.\\

\noindent {\bf XAVIER RUBIO-CAMPILLO} is Researcher in Computer Applications in Science and Engineering, Barcelona Supercomputing Center. He has a transdisciplinary training of Computer Science (BSc) and Humanities (PhD) with a strong emphasis on the study of past societies using historical and archaeological contexts. His main research line is the application of formal models to explore the processes of cultural evolution in past societies. His email address is \email{xavier.rubio@bsc.es}.\\
